Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-08-10 analysis/paper/Rmd/hotspot-one-chromosome.Rmd
replaced heatmaply call with pheatmap

pm[ord, ord] %>% # order both cols and rows by 'ord'
  apply(FUN = trunc2, MARGIN = 2, threshold = 5) %>%
  heatmaply:::heatmaply(Rowv = FALSE,
            Colv = FALSE,
            plot_method = "plotly",
            symm = TRUE,
            row_side_colors = as.matrix(annots_ord[[3]][, 2:3]),
            fontsize_col = 2,
            fontsize_row = 2,
            ) %>%
  hide_guides()
```

>>>>

pm[ord, ord] %>% # order both cols and rows by 'ord'
  apply(FUN = trunc2, MARGIN = 2, threshold = 5) %>%
  pheatmap::pheatmap(cluster_rows = FALSE,
                     cluster_cols = FALSE,
                     fontsize = 2,
                     annotation_row = as.data.frame(annfoo)
                     )
```
